---
title: 'Lab10'
author: "Hoa Hoang"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments 
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

## Task 1
```{r}
getwd()
```

## Task 2
```{r}
#max likelihood function  
## For repeated sampling from same distribution                     
mymaxlik=function(lfun,x,param,...){
# how many param values are there?
np=length(param)
# outer -- notice the order, x then param
# this produces a matrix -- try outer(1:4,5:10,function(x,y) paste(x,y,sep=" "))   to understand
z=outer(x,param,lfun) #A
# z is a matrix where each x,param is replaced with the function evaluated at those values
y=apply(z,2,sum)

# y is a vector made up of the column sums
# Each y is the log lik for a new parameter value
plot(param,y,col="Blue",type="l",lwd=2,...)
# which gives the index for the value of y == max.
# there could be a max between two values of the parameter, therefore 2 indices
# the first max will take the larger indice
i=max(which(y==max(y))) #B
abline(v=param[i],lwd=2,col="Red")

# plots a nice point where the max lik is
points(param[i],y[i],pch=19,cex=1.5,col="Black")
axis(3,param[i],round(param[i],2))
#check slopes. If it is a max the slope shoud change sign from + to 
# We should get three + and two -vs
ifelse(i-3>=1 & i+2<=np, slope<-(y[(i-2):(i+2)]-y[(i-3):(i+1)])/(param[(i-2):(i+2)]-param[(i-3):(i+1)]),slope<-"NA")
return(list(i=i,parami=param[i],yi=y[i],slope=slope))
}

```

### Code Explaination
Line A gives the outer product of the arrays X and param, using lfun as the function
Line B assigns the max value of y to i

### Binomial Experiment
$$L(p)=p(y_1)p(y_2)...p(y_8)$$
$$= {20 \choose y_1} p^{y_1}q^{20-y_1} * {20 \choose y_2} p^{y_2}q^{20-y_2} ... {20 \choose y_8} p^{y_8}q^{20-y_8}$$
$$= \prod_1^8 {20 \choose y_i} p^{y_i}q^{20-y_i}$$
### What is the R code for the abovelikelihood?   
dbinom(y1,20,p) * ... * dbinom(y8,20,p)

### Find the maximum likelihood estimate when the following is the data y=3,3,4,3,4,5,5,4 (record the plot).
```{r}
y=c(3,3,4,3,4,5,5,4)
logbin= function(x,p){
  log(dbinom(x,prob=p,size=20))
}
mymaxlik(lfun=logbin,x=y,param=seq(0,1,length=1000),main = "Binomial, n = 20")
```

0.2 is the estimate

## Task 3
### The graphical solution using mymaxlik()
```{r}
y=c(4,6,7,6,5)
logpois= function(x,l){
  log(dpois(x,lambda = l))
}
mymaxlik(lfun=logpois,x=y,param=seq(0,10,length=1000),main = "Pois")
```

5.6 is the estimate 

### Using myNRML() 
```{r}
myNRML=function(x0,delta=0.001,llik,xrange,parameter="param"){
f=function(x) (llik(x+delta)-llik(x))/delta
fdash=function(x) (f(x+delta)-f(x))/delta
d=1000
i=0
x=c()
y=c()
x[1]=x0
y[1]=f(x[1])
while(d > delta & i<100){
i=i+1
x[i+1]=x[i]-f(x[i])/fdash(x[i])
y[i+1]=f(x[i+1])
d=abs(y[i+1])
}
layout(matrix(1:2,nr=1,nc=2,byrow=TRUE),width=c(1,2))
curve(llik(x), xlim=xrange,xlab=parameter,ylab="log Lik",main="Log Lik")
curve(f(x),xlim=xrange,xaxt="n", xlab=parameter,ylab="derivative",main=  "Newton-Raphson Algorithm \n on the derivative")
points(x,y,col="Red",pch=19,cex=1.5)
axis(1,x,round(x,2),las=2)
abline(h=0,col="Red")

segments(x[1:(i-1)],y[1:(i-1)],x[2:i],rep(0,i-1),col="Blue",lwd=2)
segments(x[2:i],rep(0,i-1),x[2:i],y[2:i],lwd=0.5,col="Green")

list(x=x,y=y)
}

logpois= function(x){
  log(dpois(4,x))+log(dpois(6,x))+log(dpois(7,x))+log(dpois(6,x))+log(dpois(5,x))
}

myNRML(x0=0.1,delta=0.00001, llik = logpois, xrange=c(4,7),param="lambda")
```

5.6 is still the estimation

## Task 4
### Use mymaxlikg() to find p
```{r}

## Joint density has one unknown common parameter but different values for the other parameters
## We need only make L(theta)

logbin2=function(theta){log(dbinom(2,prob=theta,size=6)) + log(dbinom(4,prob=theta,size=10))}

mymaxlikg=function(lfun="logbin2",theta) { # default log lik is a combination bin
nth=length(theta)  # nu. of valuse used in theta
thmat=matrix(theta,nr=nth,nc=1,byrow=TRUE) # Matrix of theta
z=apply(thmat,1,lfun) # z holds the log lik values
zmax=max(which(z==max(z)))  # finding the INDEX of the max lik
plot(theta,exp(z),type="l") # plot of lik
abline(v=theta[zmax],col="Blue")   #  verical line through max
axis(3,theta[zmax],round(theta[zmax],4))  # one tick on the third axis 
theta[zmax]   # theta corresponding to max lik
}

mymaxlikg(theta=seq(0,1,length=10000))
```

## Task 5
### The algebraic expression 
$$L(\theta_1,\theta_2)= {n \choose y_1}\theta_1^{y_1}(1-\theta_1)^{n-y_1}*\frac{e^{-\theta_2}\theta_2^{y_2}}{y_2!}$$
$$l(\theta_1,\theta_2)= log(n!)-log(y_1!)-log([n-y_1]!)+y_1log(\theta_1)+(n-y_1)log(1-\theta_1)-\theta_2(1)+y_2log(\theta_2)-log(y_2!)$$

### Using mymaxlikg2
```{r}

logbinpois=function(theta1,theta2){
  log(dbinom(4,size=20,prob=theta1)) + log(dpois(3,lambda=theta2))
} 

maxlikg2=function(theta1,theta2,lfun="logbinpois",...){
n1=length(theta1)
n2=length(theta2)
z=outer(theta1,theta2,lfun)
contour(theta1,theta2,exp(z),...) # exp(z) gives the lik
maxl=max(exp(z))    # max lik
coord=which(exp(z)==maxl,arr.ind=TRUE)  # find the co-ords of the max
th1est=theta1[coord[1]] # mxlik estimate of theta1
th2est=theta2[coord[2]]
abline(v=th1est,h=th2est)
axis(3,th1est,round(th1est,2))
axis(4,th2est,round(th2est,2),las=1)
list(th1est=th1est,th2est=th2est)
}
maxlikg2(theta1=seq(0,1,length=1000),theta2=seq(0,10,length=1000),nlevels=20)
```

## Task 6
```{r}
mymlnorm=function(x,mu,sig,...){  #x sample vector
nmu=length(mu) # number of values in mu
nsig=length(sig)
n=length(x) # sample size
zz=c()    ## initialize a new vector
lfun=function(x,m,p) log(dnorm(x,mean=m,sd=p))   # log lik for normal
for(j in 1:nsig){
z=outer(x,mu,lfun,p=sig[j]) # z a matrix 
# col 1 of z contains lfun evaluated at each x with first value of mu, 
# col2 each x with 2nd value of m 
# all with sig=sig[j]
y=apply(z,2,sum)
# y is a vector filled with log lik values, 
# each with a difft mu and all with the same sig[j]
zz=cbind(zz,y)
## zz is the matrix with each column containing log L values, rows difft mu, cols difft sigmas 
}
maxl=max(exp(zz))
coord=which(exp(zz)==maxl,arr.ind=TRUE)
maxlsig=apply(zz,1,max)
contour(mu,sig,exp(zz),las=3,xlab=expression(mu),ylab=expression(sigma),axes=TRUE,
main=expression(paste("L(",mu,",",sigma,")",sep="")),...)
mlx=round(mean(x),2)  # theoretical
mly=round(sqrt((n-1)/n)*sd(x),2)
#axis(1,at=c(0:20,mlx),labels=sort(c(0:20,mlx)))
#axis(2,at=c(0:20,mly),labels=TRUE)
abline(v=mean(x),lwd=2,col="Green")
abline(h=sqrt((n-1)/n)*sd(x),lwd=2,col="Red")

# Now find the estimates from the co-ords
muest=mu[coord[1]]
sigest=sig[coord[2]]

abline(v=muest, h=sigest)
return(list(x=x,coord=coord,maxl=maxl))
}
mymlnorm(x=c(10,12,13,15,12,11,10 ),mu=seq(10,15,length=1000),sig=seq(0.1,4,length=1000),lwd=2,labcex=1)
```

## Task 7
```{r}
mymlbeta=function(x,alpha,beta,...){  #x sample vector
na=length(alpha) # number of values in alpha
nb=length(beta)
n=length(x) # sample size
zz=c()    ## initialize a new vector
lfun=function(x,a,b) log(dbeta(x,shape1=a,shape2=b))   # log lik for beta
for(j in 1:nb){
z=outer(x,alpha,lfun,b=beta[j]) # z a matrix 
# col 1 of z contains lfun evaluated at each x with first value of alpha, 
# col2 each x with 2nd value of a 
# all with b=beta[j]
y=apply(z,2,sum)
# y is a vector filled with log lik values, 
# each with a difft alpha and all with the same sig[j]
zz=cbind(zz,y)
## zz is the matrix with each column containing log L values, rows difft alpha, cols difft betas 
}
maxl=max(exp(zz))    # max lik
coord=which(exp(zz)==maxl,arr.ind=TRUE)  # find the co-ords of the max
aest=alpha[coord[1]] # mxlik estimate of alpha
best=beta[coord[2]]
contour(alpha,beta,exp(zz),las=3,xlab=expression(alpha),ylab=expression(beta),axes=TRUE,
main=expression(paste("L(",alpha,",",beta,")",sep="")),...)

abline(v=aest, h=best)
points(aest,best,pch=19)
axis(4,best,round(best,2),col="Red")
axis(3,aest,round(aest,2),col="Red")
return(list(x=x,coord=coord,maxl=maxl,maxalpha=aest,maxbeta=best))
}

mymlbeta(x=rbeta(30,shape1=3,shape2=4),alpha=seq(1,4,length=100),beta=seq(2,8,length=100),lwd=2,labcex=1)

z=c()
a=3
b=4
sam= rbeta(30,shape1=a,shape2=b)
nsam=length(sam)
for(i in 1:12){
w=mymlbeta(x=sample(sam,nsam,replace=TRUE),alpha=seq(0.1,20,length=100),beta=seq(0.1,20,length=100),lwd=2,labcex=1,col="steelblue")
points(a,b,col="Red",pch=19)
abline(v=a,h=b,col="Red")
z<-rbind(z,c(w$maxalpha,w$maxbeta))
 }
colnames(z)=c("alpha","beta")
z
dz=apply(z-c(a,b),1,function(x) sqrt(sum(x^2)) )
plot(dz)
which(dz>4)
```

## Task 8
```{r}
mypackage::mymlnorm(x=c(1,2,3,4,5),mu=seq(1,5,length=1000),sig=seq(0.1,4,length=1000),lwd=2,labcex=1)
```

