---
title: 'Assignemnt 2'
author: "Hoa Hoang"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```
## Completed
17/17

## Q1 MS 3.36 pg 105-106
### a.
$P(ExpertFail | Match) = 1 - P(ExpertSuccess|Match)$
```{r}
1-(92.12/100)
```
### b.
$P(NoviceFail | Match) = 1 - P(NoviceSuccess|Match)$
```{r}
1-(74.55/100)
```

### c. 
Given the answer from part a and b, the participant that fail is more likely is a novice

## Q2 MS 3.52 - pg 111

$P(E1) = 0.3$

$P(E2) = 0.2$

$P(E3) = 0.5$

$P(error|E1) = 0.01$

$P(error|E2) = 0.03$

$P(error|E3) = 0.02$

### a. 

$P(E1 | error) = \frac{P(E1)P(error|E1)}{P(E1)P(error|E1)+P(E2)P(error|E2)+P(E3)P(error|E3)}$
```{r}
(0.3*0.01)/(0.3*0.01+0.2*0.03+0.5*0.02)
```

### b. 

$P(E2 | error) = \frac{P(E2)P(error|E2)}{P(E1)P(error|E1)+P(E2)P(error|E2)+P(E3)P(error|E3)}$
```{r}
(0.2*0.03)/(0.3*0.01+0.2*0.03+0.5*0.02)
```

### c. 
$P(E3 | error) = \frac{P(E3)P(error|E3)}{P(E1)P(error|E1)+P(E2)P(error|E2)+P(E3)P(error|E3)}$
```{r}
(0.5*0.02)/(0.3*0.01+0.2*0.03+0.5*0.02)
```

### d. 

Engineer #3

## Q3 MS Theorem 3.1 - pg 113
With two digit, we have 2^2 = 4, is number of possible values  
With three digit, we have 2^3 = 8, is number of possible values 
With n digit, we have 2^n possible values 

## Q4 MS Theorem 3.2 - pg 114
Given three balls, black(B), white(W), and yellow(Y). If we want the possible combination of them without picking, then:

At first we have 3 ways to pick any ball.   
Then next, we have 2 ways of picking the ball (Since we do not replace the picked ball).   
Finally, we pick the last ball.

Possible ways: 3 * 2 * 1 = 6 (BWY, BYW, WBY, WYB, YBW, YWB)
Which is the same as $\frac{N!}{N - n!}=\frac{3!}{(3 - 3)!} = \frac{3*2*1}{1} = 6$

## Q5 MS Theorem 3.3 - pg 116
If we have N elemnets in a set   
Let A be the number of way partition N distinctly different elements into k sets
By theorm 3.2, we have N! way to arrange the elements in N position
And by theorm 3.1, we have $A*n_1!n_2!...n_k!$   
Therefore, N distinctly different elementsin k positions is $A=\frac{N!}{n_1!n_2!...n_k!}$

## Q6 MS Theorem 3.4 - pg 117
Selecting n element is N elements is the same as partitioning into 2 sets, $\frac{N!}{n!(N-n)!}$, as proven by theorm 3.3

## Q7 MS 4.2 - pg 138
### a.
```{r}
.09+.30+.37+.20+.04
```

### b. 
```{r}
.20+.04
```

### c.
```{r}
.30+.09
```

## Q8 MS 4.12 - pg 143
### a. 
All p(y) is less than or equal to 1 and greater than or equal to 0
```{r}
.17+.10+.11+.11+.10+.10+.07+.05+.03+.02+.02+.02+.02+.02+.01+.01+.01+.01+.01+.005+.005
```

### b. 
```{r}
.02+.02+.02+.02+.01+.01+.01+.01+.01+.005+.005
```

### c. 
```{r}
#mean
m=0*.17+1*.10+2*.11+3*.11+4*.10+5*.10+6*.07+7*.05+8*.03+9*.02+10*.02+11*.02+12*.02+13*.02+14*.01+15*.01+16*.01+17*.01+18*.01+19*.005+20*.005
m
# Σx2p − μ2
v=(0^2*.17+1^2*.10+2^2*.11+3^2*.11+4^2*.10+5^2*.10+6^2*.07+7^2*.05+8^2*.03+9^2*.02+10^2*.02+11^2*.02+12^2*.02+13^2*.02+14^2*.01+15^2*.01+16^2*.01+17^2*.01+18^2*.01+19^2*.005+20^2*.005) - m^2
v
```

### d. 
```{r}
# Chebyshev: At least 75% of the data lie within two standard deviations of the mean
from = m-2*sqrt(v)
if(from<0){
  from = 0;
}
from
to = m+2*sqrt(v)
to
```

## Q9 MS 4.34 - pg 154
### a. 
```{r}
dbinom(10,25,.7)
```

### b. 
```{r}
pbinom(5,25,.7)
```

### c.
```{r}
#mean
25*0.7
#sd
sqrt(25*0.7*0.3)
```

### d.
It is expected 17 or 18 in 25 PhD are foreign nationals
With the calculated sd, we can use emperical rule to to guess the distribution using the range within 1,2,3 sd

## Q10 MS 4.46 - pg 158
### a.
to each of the 10 tracks?
```{r}
#probability of 5 trains in a track if having onlny one track
p=5/50
#probability of 5 trains in every track, from formula
factorial(50)/(factorial(5)^10) * (p^5)^10 
#OR dmultinom(c(5,5,5,5,5,5,5,5,5,5), 50, c(0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1))

```

### b. 
```{r}
# number of ways 0 train on the track 1 = number of ways all trains on other tracks
a = 9^50  # 9 other tracks and n = 50
# number of ways 1 train on the track 1
b = 50 * 9^49 # 50 choose 1 and 49 train left to make combinations in other tracks
(a+b)/10^50 # 10^50 is the total ways
```

## Q11 MS 4.54 - pg 162
### a.
This is a geometric distribution so $P(Y)=pq^{y-1}$

### b.

```{r}
#probabbility of other reasons and q
p=(12+6+4+18)/100
q = 1-p
#means
1/p
```
It means on avarage, we must interview 2.5 people until we found one that say "green" not because of label or packaging

### c. 
```{r}
p*(q)^0
```

### d.
```{r}
1-p*(q-1)^0 - p*(q)^1
```

## Q12 MS 4.66 - pg 168
### a. 
```{r}
#This is hyper distribution
n=10
N=209
r=8
p=r/n
m=(n*p)/N
m
```

### b.
```{r}
dhyper(4,r,N-r,n)
```

## Q13 MS 4.78 - pg 173
### a. 
```{r}
#This is poisson distribution so lambda is the mean
l=0.03
l
```

### b. 
Probability of an interval is independent of others'   
Probability of an interval does not change over different intervals.   

### c. 
```{r}
dpois(0,l)
```
|
## Q14 MS 5.2 - pg 191
### a.
$\int_{0}^{1}c(2-y)dy=1$   
$1=c\int_{0}^{1}(2-y)dy$   
$1=c|2y-\frac{y^2}{2}|^1_0$   
$1=c(2-\frac{1}{2})$   
$c=\frac{2}{3}$   

### b.
$F(y)=\int_{0}^{y}c(2-y)dy$   
$F(y)=\frac{2}{3}|2y-\frac{y^2}{2}|^y_0$   
$F(y)=\frac{2}{3}(2y-\frac{y^2}{2})$   

### c.
$F(0.4)=\frac{2}{3}(2*0.4-\frac{0.4^2}{2})$
```{r}
(2/3)*(2*0.4-((0.4^2)/2))
```

### d.
$P(.1 \leq y \leq .6)=F(0.6)-F(0.1)$   
```{r}
(2/3)*(2*0.6-((0.6^2)/2)) - (2/3)*(2*0.1-((0.1^2)/2))
```

## Q15 MS 5.10 - pg 196
### a.
Mean   
$E(y)=\int_{-5}^{5}y*\frac{3}{500}(25-y^2)dy$    
$E(y)=\frac{3}{500}|(\frac{25y^2}{2}-\frac{y^4}{4})|^5_{-5}$   
$E(y)=0$

Variance   
$E(y^2)=\int_{-5}^{5}y^2*\frac{3}{500}(25-y^2)dy$   
$E(y^2)=\frac{3}{500}|(\frac{25y^3}{3}-\frac{y^5}{5})|^5_{-5}$  
$E(y^2)=\frac{3}{500}(\frac{25*5^3}{3}-\frac{5^5}{5}) - (\frac{25*(-5)^3}{3}-\frac{(-5)^5}{5})$   
$E(y^2)=\frac{3}{500}(\frac{3125}{3}-\frac{3125}{5}) - (\frac{-3125}{3}-\frac{-3125}{5})$   
$E(y^2)=\frac{3}{500}(\frac{6250}{3}-\frac{6125}{5})$ 
$E(y^2)=5$   
$V(y)=E(y^2)-E(y)^2$   
$V(y)=5-0 =5$


### b.
E(y) is still 0   
Since 1 hr = 60 mins   
$V(60y)=60^2V(y)=3600*5=18000$   

### c.
E(y) is still 0   
Since 1 second = 1/60 min   
$V(y/60)=\frac{V(y)}{60^2}=\frac{5}{3600}=0.001388889$  

## Q16 MS 5.36 - pg 205
```{r}
m=50
sd=3.2
#Normal distribution
```
### a.
```{r}
z=(45-m)/sd
1-pnorm(z)
```

### b.
```{r}
z=(55-m)/sd
pnorm(z)
```

### c.
```{r}
z1=(51-m)/sd
z2=(52-m)/sd
pnorm(z2)-pnorm(z1)
```

## Q17 MS 5.38- pg 205
```{r}
m=605
sd=185
```

### a. 
```{r}
z1=(500-m)/sd
z2=(700-m)/sd
pnorm(z2)-pnorm(z1)
```

### b. 
```{r}
z1=(400-m)/sd
z2=(500-m)/sd
pnorm(z2)-pnorm(z1)
```
### c. 
```{r}
z=(850-m)/sd
pnorm(z)
```

### d. 
```{r}
z=(1000-m)/sd
1-pnorm(z)
```

### e. 
```{r}
m + sd*(1.28) #1.28 from Appendix B Table 5 
```

