---
title: 'Lab11'
author: "Hoa Hoang"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments 
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

## Task 1
```{r}
getwd()
```

## Task 2
```{r}
d=c(5.0581, 4.9707, 5.0893, 4.9334, 4.9777, 5.0285, 4.8555, 4.9565, 
4.9769, 4.9722, 4.999, 4.9925, 4.9686, 5.0662, 4.9239, 4.9781, 
5.0485, 5.0014, 4.9957, 5.0195, 5.0118, 4.9928, 5.0361, 5.0185, 
4.9879)
```

### CI for the mean
```{r}
#95%
left=mean(d)-qt(1-0.05/2,length(d)-1)*(sd(d)/sqrt(length(d)))
right=mean(d)+qt(1-0.05/2,length(d)-1)*(sd(d)/sqrt(length(d)))
sprintf("%f to %f",left,right)

#90%
left=mean(d)-qt(1-0.1/2,length(d)-1)*(sd(d)/sqrt(length(d)))
right=mean(d)+qt(1-0.1/2,length(d)-1)*(sd(d)/sqrt(length(d)))
sprintf("%f to %f",left,right)

#80%
left=mean(d)-qt(1-0.2/2,length(d)-1)*(sd(d)/sqrt(length(d)))
right=mean(d)+qt(1-0.2/2,length(d)-1)*(sd(d)/sqrt(length(d)))
sprintf("%f to %f",left,right)

#50%
left=mean(d)-qt(1-0.5/2,length(d)-1)*(sd(d)/sqrt(length(d)))
right=mean(d)+qt(1-0.5/2,length(d)-1)*(sd(d)/sqrt(length(d)))
sprintf("%f to %f",left,right)
```

### CI for the variance
```{r}
#95%
df=length(d)
a=0.05
left=df*var(d)/qchisq(1-a/2,df)
right=df*var(d)/qchisq(a/2,df)
sprintf("%f to %f",left,right)

#90%
df=length(d)
a=0.1
left=df*var(d)/qchisq(1-a/2,df)
right=df*var(d)/qchisq(a/2,df)
sprintf("%f to %f",left,right)

#80%
df=length(d)
a=0.2
left=df*var(d)/qchisq(1-a/2,df)
right=df*var(d)/qchisq(a/2,df)
sprintf("%f to %f",left,right)

#50%
df=length(d)
a=0.5
left=df*var(d)/qchisq(1-a/2,df)
right=df*var(d)/qchisq(a/2,df)
sprintf("%f to %f",left,right)
```

## Task 3
```{r}
blue=c(21.65, 17.48, 20.1, 21.57, 14.82, 19.17, 21.08, 18.23, 22.93, 
15.66, 20.89, 21.66, 18.5, 20.59, 18.63, 18.91, 19.53, 17.7, 16.5, 19.03)
snapper=c(31.65, 27.48, 30.1, 31.57, 24.82, 29.17, 31.08, 28.23, 32.93, 
25.66, 30.89, 31.66, 28.5, 30.59, 28.63)
```

### 95% CI Using Calculator
Since the lenghts are less than 30, we use the second formula
```{r}
a=0.05
n1=length(snapper)
n2=length(blue)
df=n1+n2-2
sp=((n1-1)*var(snapper)+(n2-1)*var(blue))/(df)
left=mean(snapper)-mean(blue)-qt(1-a/2,df)*sqrt(sp*(1/n1+1/n2))
right=mean(snapper)-mean(blue)+qt(1-a/2,df)*sqrt(sp*(1/n1+1/n2))
sprintf("%f to %f",left,right)
```

It means that snapper is bigger than blue, ranging from 8.76 to 11.84 units 

### Using t.test()
```{r}
#95%
t.test(snapper,blue,var.equal = TRUE,conf.level = 0.95)$conf.int

#85%
t.test(snapper,blue,var.equal = TRUE,conf.level = 0.9)$conf.int

#75%
t.test(snapper,blue,var.equal = TRUE,conf.level = 0.80)$conf.int 

#25%
t.test(snapper,blue,var.equal = TRUE,conf.level = 0.25)$conf.int 
```

As interval as the confidence level decreases, the range get bigger

## Task 4
```{r}
Exam1=c(40.98, 59.36, 46.69, 41.8, 61.63, 65.31, 62.96, 60.21, 56.89, 
78.41, 53.44, 75.2, 60.54, 52.43, 41.41, 70.79, 73.55, 55.65, 
61.43, 63.84, 58.07, 53.79, 54.45, 67.18, 44.46)
Exam2=c(50.22, 66.19, 58.75, 51.88, 66.61, 70.86, 74.25, 70.23, 69.55, 
87.18, 63.62, 81.7, 70.5, 66.02, 51.35, 80.92, 85.65, 65.44, 
74.37, 75.28, 67.86, 59.92, 64.42, 73.57, 57.15)
exdif=Exam1-Exam2
```

Since the lenght is less than 30, we use the second formula
```{r}
a=0.05
n=length(exdif)
left=mean(exdif)-qnorm(1-a/2)*sd(exdif)/sqrt(n)
right=mean(exdif)+qnorm(1-a/2)*sd(exdif)/sqrt(n)
sprintf("%f to %f",left,right)
```

It means Exam 1 score is lower than Exam 2 by 8.76 to 10.68 

### Using t.test()
```{r}
#90%
t.test(exdif,conf.level = 0.9)$conf.int

#80%
t.test(exdif,conf.level = 0.8)$conf.int

#70%
t.test(exdif,conf.level = 0.7)$conf.int 

#60%
t.test(exdif,conf.level = 0.6)$conf.int 

#10%
t.test(exdif,conf.level = 0.1)$conf.int 
```

## Task 5
```{r}
file = read.csv("NZBIRDS.csv")
addmargins(with(file,table(Extinct,Flight)))
```

### 95% CI of the different
```{r}
#1 for non-extinct, 2 for extinct
a=0.05
n1=78
n2=38
p1=7/78
p2=21/38
e1=(p1*(1-p1))/n1
e2=(p2*(1-p2))/n2
left=(p1-p2)-qnorm(1-a/2)*sqrt(e1+e2)
right=(p1-p2)+qnorm(1-a/2)*sqrt(e1+e2)
sprintf("%f to %f",left,right)
```

## Task 6
### Using calculator
```{r}
set.seed(35);sam1=rnorm(25,mean=10,sd=5)
set.seed(45);sam2=rnorm(34,mean=40,sd=8)
a=0.05
ci=c()
ci[1]=var(sam1)/(var(sam2)*((qf(1-a/2, df1=24,df2=33))))
ci[2]=var(sam1)/var(sam2)*((qf(1-a/2, df1=33,df2=24)))
```

### Using var.test()
```{r}
#80%
var.test(sam1,sam2,conf.level = 0.8)
#70%
var.test(sam1,sam2,conf.level = 0.7)
#60%
var.test(sam1,sam2,conf.level = 0.6)
#50%
var.test(sam1,sam2,conf.level = 0.5)
```

## Task 7
```{r}
set.seed(23);x = rnorm(30,mean=10,sd=12)
mypackage::myci(x)
```

