---
title: "Lab1"
author: "Hoa Hoang"
date: 1/13/2020
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1
```{r}
getwd()
```
## Task 2
```{r}
ddt <- read.csv("DDT.csv")
head(ddt,6)

```
## Task 3
#### 1. Qualitative variables are RIVERS and SPECIES
#### 2. Quanlitative variables are MILES, LENGTH, WEIGHT, and DDT
#### 3. There are 3 species: CCATFISH, SMBUFFALO,and LMBASS
#### 4.
```{r}
  new1 <- subset(ddt, SPECIES =='LMBASS' & WEIGHT >800)
  new1
```
#### 5.
```{r}
  new2 <- subset(ddt, RIVER =='SCM' & DDT >4)
  new2
```
## Task 4
#### Q1: 42.8125
```{r}
  mean_LENGTH <-with(ddt,mean(LENGTH))
  mean_LENGTH
```
#### Q2: 376.5461
```{r}
  sd_WEIGHT<-with(ddt,sd(WEIGHT))
  sd_WEIGHT
```
#### Q3: NO
```{r}
with(ddt,plot(WEIGHT,LENGTH))
```

#### Q4: The answer is 1
```{r}
v<-1:20
v/20
```
## Task 4
#### Make a table of the rivers.
```{r}
  river_table<-with(ddt,table(RIVER))
  river_table
```

#### Make a color coded barplot of the rivers.
```{r}
  barplot(river_table,col=rainbow(7))
```

#### Make a table of the rivers crossed with the species of fish.
```{r}
  river_n_fish_table <- with(ddt,table(RIVER,SPECIES))
  river_n_fish_table
```

#### Make a barplot of the rivers crossed with the species of fish
```{r}
  barplot(river_n_fish_table,legend = TRUE, col=rainbow(4))
```

## Task 5
#### Make a pie chart of Fish SPECIES
```{r}
  species_table<-with(ddt,table(SPECIES))
  with(ddt,pie(species_table))
```

#### Make a pie chart of RIVERS
```{r}
  with(ddt,pie(river_table))
```

## Task 6
#### Make a boxplot of the variable DDT
```{r}
  with(ddt,boxplot(DDT))
```

#### Make a boxplot of the variable WEIGHT
```{r}
  with(ddt,boxplot(WEIGHT))
```

#### Make a boxplot of the variable LENGTH
```{r}
  with(ddt,boxplot(LENGTH))
```

## Task 7 
#### Make a coplot of LENGTH Vs WEIGHT given RIVER
```{r}
  with(ddt,coplot(LENGTH ~ WEIGHT | RIVER))
```

#### Make a coplot of DDT Vs WEIGHT given SPECIES
```{r}
  with(ddt,coplot(DDT ~ WEIGHT | SPECIES))
```

## Task 8
#### The box plot
```{r}
  library(ggplot2)
  g <- ggplot(ddt, aes(x=SPECIES, y=WEIGHT,fill = RIVER)) +
  ggtitle("HOA HOANG")+
  geom_boxplot()
  g

```

#### The violin plot
```{r}
  g <- ggplot(ddt, aes(x=RIVER, y=LENGTH,fill = SPECIES)) +
  ggtitle("HOA HOANG")+
  geom_violin()
  g
```

#### The scatter plot
```{r}
  g <- ggplot(ddt, aes(x=WEIGHT, y=LENGTH, color = SPECIES)) +
  ggtitle("HOA HOANG")+
  geom_point()
  g
```

