---
title: "Lab5"
author: "Hoa Hoang"
date: "2/12/2020"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

## Task 1
```{r}
getwd()
```

## Task 2
### Simulate a binomial experiment where n=10,p=0.7, and Y=number of successes.
```{r}
mybin=function(iter,n, p, flag=FALSE){ 
  sam.mat=matrix(NA,nr=n,nc=iter, byrow=TRUE)
  succ=c()
  for( i in 1:iter){
    sam.mat[,i]=sample(c(1,0),n,replace=TRUE, prob=c(p,1-p))
    succ[i]=sum(sam.mat[,i])
  }
  succ.tab=table(factor(succ,levels=0:n))
  if(flag==TRUE){
    print(succ.tab)
  }
  barplot(succ.tab/(iter), col=rainbow(n+1), main="Binomial simulation", xlab="Number of successes")
  print(succ.tab/iter)
}
```


###	Record the plots for each of the following (Use color)
```{r}
mybin(100,10,0.7)
mybin(200,10,0.7)
mybin(500,10,0.7)
mybin(1000,10,0.7)
```

### For the last simulation (10,000 iterations) copy and paste the table that is produced from the function.
```{r}
mybin(10000,10,0.7,TRUE) 
```
### Verify that each value in the table is approximately correct using dbinom() – you will need to look up the function using ?dbinom
```{r}
dbinom(1:10,10,0.7)
```
  > Yes, approximately correct

## Task 3
### Suppose that there is a bag of 20 marbles, 12 white (“1”) and 8 black “0”. Create a sample of size n=5 without replacement
```{r}
sample(c("0","0","0","0","0","0","0","0",
         "1","1","1","1","1","1","1","1","1","1","1","1")
       ,size=5)
```

### Now do the same with replace=TRUE.
```{r}
sample(c("0","1"),size=5,replace=TRUE)
```

###	Use the function myhyper(), on CANVAS, assume Y = number of whites, remember sampling is without replacement, n=5. 
```{r}
myhyper=function(iter=100,N=20,r=12,n=5,flag=FALSE){
# make a matrix to hold the samples
#initially filled with NA's
sam.mat=matrix(NA,nr=n,nc=iter, byrow=TRUE)
#Make a vector to hold the number of successes over the trials
succ=c()
for( i in 1:iter){
#Fill each column with a new sample
sam.mat[,i]=sample(rep(c(1,0),c(r,N-r)),n,replace=FALSE)
#Calculate a statistic from the sample (this case it is the sum)
succ[i]=sum(sam.mat[,i])
}

#Make a table of successes
succ.tab=table(factor(succ,levels=0:n))
if(flag==TRUE){
  print(succ.tab)
}
#Make a barplot of the proportions
barplot(succ.tab/(iter), col=rainbow(n+1), main="HYPERGEOMETRIC simulation", xlab="Number of successes")
succ.tab/iter
}

```
### Use this code to make barplots of Y for the following number of iterations
```{r}
myhyper()
myhyper(iter=200)
myhyper(iter=500)
myhyper(iter=1000)
```

### For the last simulation (10,000 iterations) copy and paste the table that is produced from the function.
```{r}
myhyper(iter=10000,flag=TRUE)
```

### Verify that each value in the table is approximately correct using dhyper()
```{r}
dhyper(x=0:5, m=12, n=8, k=5)
```
  > Values are very close
  
## Task 4
### In lab5.r there is a function called mysample(). Look at the code and describe what you think it should do – record your response here.
```{r}
mysample=function(n, iter=10,time=0.5){
  for( i in 1:iter){
    #make a sample
    s=sample(1:10,n,replace=TRUE)
    # turn the sample into a factor
    sf=factor(s,levels=1:10)
    #make a barplot
    barplot(table(sf)/n,beside=TRUE,col=rainbow(10), 
    main=paste("Example sample()", " iteration ", i, " n= ", n,sep="") ,
    ylim=c(0,0.2))
    #release the table
    ##Sys.sleep(time)
  }
}
```
  >This function is making samplings between number 1 to 10. number of iterration is depending on the user input.
  >Then it make a graph out of the probability of the numbers. The graph y axis is limited between 0 and 0.2
  
### Run the function with the following arguments mysample(n=1000, iter=30,time=1)
```{r}
  mysample(n=1000, iter=30,time=1)
```

###	Describe what you see here.
  > I see 30 iterations of samplings between number 1 to 10, portray with thier probability of appearance
  
## Task 5
###	Use R to calculate 
#### 8 choose 4	
```{r}
choose(8,4)
```

#### P(Y>4),Y~Pois(λ=2)
```{r}
ppois(4,2,lower.tail = FALSE)
```

###	Some more calculations in R
####	P(Y=10),Y~NegBin(p=0.4,r=3) see CANVAS which has a full explanation of this.

```{r}
#  This means that in R we need n=3 (size), x=y-r=10-3=7
dnbinom(7,3,0.4)  # Nu Failures, Nu of successes, prob success
mynbin=function(y,r,p){
  choose(y-1,r-1)*p^r*(1-p)^(y-r)
}
mynbin(10,3,0.4)
```

####	P(Y≤8),Y~Bin(n=15,p=0.4)
```{r}
  pbinom(8,15,0.4)
```

## Task 6
### Create an R function by copying code from this lab. 
### Document the function using roxygen
### Place the function into your package
### Install and restart the package using the icon in R studio 
### Invoke the function by doing the following – suppose your function is called myf()
```{r}
mypackage::mybin(50,5,0.5)
```




