---
title: 'Assignemnt 3'
author: "Hoa Hoang"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

## Completed
16/16

## Q1 MS 5.54 - pg 215
```{r}
data=read.csv("PHISHING.csv")
```

### a.

$$P(x \geq 120)=e^{-120/95}$$
```{r}
cat("The probability:", exp(-120/95))
```

### b.
```{r}
mean=mean(data$INTTIME,na.rm=T)
cat("The mean:", mean)
var=var(data$INTTIME,na.rm=T)
cat("The variance:", var)
```

With the mean is exactly 95, and the variance is very close to 95^2, this data appear to follow an exponential distribution with β=95

## Q2 5.56 - Page 215
```{r}
a=3
b=0.07
```

### a. 
```{r}
mean=a*b
cat("The mean:", mean)
var=a*b*b
cat("The variance:", var)
```

### b. 
```{r}
lower = mean-3*sqrt(var)
lower
upper = mean+3*sqrt(var)
upper
```

It is very unlikely for the value to be as high as .60 million cubic feet per second. Since three standard deviations account for about 99.7% and .60 is outside of 3 standard deviations

## Q3 MS 5.60 - Page 216
```{r}
fA.a=2
fA.b=2
fB.a=1
fB.b=4
```

### a. 
```{r}
meanA=fA.a*fA.b
cat("The mean of Formula A:", meanA)
meanB=fB.a*fB.b
cat("The mean of Formula B:", meanB)
```

### b. 
```{r}
varA=fA.a*fA.b*fA.b
cat("The variance of Formula A:", varA)
varB=fB.a*fB.b*fB.b
cat("The variance of Formula B:", varB)
```

### c. 
```{r}
cat("The P(Y<1) of Formula A:", pgamma(1,2,scale=2))
cat("The P(Y<1) of Formula B:", pgamma(1,1,scale=4))
```

We can see that Formula B is more likely to trigger human reaction in less than 1 minute

## Q4 5.74 - Page 219
```{r}
a=2
b=4
```

### a. 
```{r}
cat("The P(Y<2):", pweibull(2,a,b^(1/a)))
```

### b. 
```{r}
mean = b^(1/a)*gamma((a+1)/a)
cat("The mean:", mean)
sd = sqrt(b^(2/a)*(gamma((a+2)/a)-(gamma((a+1)/a)^2)))
cat("The sd:", sd)
```
### c. 
```{r}
lower=mean-2*sd
cat("The lower:", lower)
lower=mean+2*sd
cat("The upper:", upper)
```

### d.
It is very not likely that Y will exceed 6 years since 6 years time period is right around 2 standards deviation

## Q5 MS 5.84 - Page 223
```{r}
a=2
b=9
```

### a.
```{r}
mean = a/(a+b)
cat("The mean:", mean)
var = (a*b)/((a+b)^2*(a+b+1))
cat("The variance:", var)
```

### b. 
```{r}
prob=1-pbeta(0.4,2,9)
cat("The P(Y>0.4):", prob)
```

### c.
```{r}
prob=pbeta(0.1,2,9)
cat("The P(Y<0.1):", prob)
```

## Q6 MS 5.114 - Page 232
### a. 
Looking at the formula giving by the book on page 217, we can see that a = 2 and b = 4
```{r}
a=2
b=16
```

### b. 
```{r}
mean = b^(1/a)*gamma((a+1)/a)
cat("The mean:", mean)
var = b^(2/a)*(gamma((a+2)/a)-(gamma((a+1)/a)^2))
cat("The variance:", var)
```

### c. 
```{r}
prob=1-pweibull(6,a,b^(1/a))
cat("The P(Y>=6):", prob)
```

## Q7 MS 6.2 - Page 239
### a.
With 2 dices, there will be 36 possiple combination (6*6). Therefore, the probability of everything is equal to 1/36

### b.
p_1(x) = 1/6 (6 possible numbers)   
p_2(y) = 1/6 (6 possible numbers)

### c.
$$p_1(x|y)=\frac{p(x,y)}{p_2(y)}=\frac{1/36}{1/6}=\frac{1}{6}$$
The same goes for $p_2(y|x)$. The result is 1/6

### d.
The answers of b and c are the same. We can conclude that the two dices are independent


## Q8 MS 6.4 - Page 240
### a. 
Counting the given table, we have

<table width="50%">
  <tr>
    <th>Y/X</th>
    <th>1</th>
    <th>2</th>
    <th>3</th>
  </tr>
  <tr>
    <td>1<br></td>
    <td>1/7</td>
    <td>2/7</td>
    <td>1/7</td>
  </tr>
  <tr>
    <td>2</td>
    <td>0</td>
    <td>0</td>
    <td>2/7</td>
  </tr>
  <tr>
    <td>3</td>
    <td>0</td>
    <td>0</td>
    <td>1/7</td>
  </tr>
</table>

### b. 
$P_1(X=1)=1/7+0+0=1/7$     
$P_1(X=2)=2/7+0+0=2/7$     
$P_1(X=3)=1/7+2/7+1/7=4/7$     

<table width="50%">
  <tr>
    <td>y</td>
    <td>1</td>
    <td>2</td>
    <td>3</td>
  </tr>
  <tr>
    <td>p1(x)</td>
    <td>1/7</td>
    <td>2/7</td>
    <td>4/7</td>
  </tr>
</table>

### c.
$P_2(Y=1)=1/7+2/7+1/7=4/7$     
$P_2(Y=2)=0+0+2/7=2/7$     
$P_2(Y=3)=0+0+1/7=1/7$     

<table width="50%">
  <tr>
    <td>x</td>
    <td>1</td>
    <td>2</td>
    <td>3</td>
  </tr>
  <tr>
    <td>p2(y)</td>
    <td>4/7</td>
    <td>2/7</td>
    <td>1/7</td>
  </tr>
</table>

### d.
$P_2(y|x) = \frac{P(x,y)}{P_1(X=x)}$   
When X = 1   
$P_2(1|1) = \frac{P(1,1)}{P_1(1)}=\frac{1/7}{1/7}=1$   
$P_2(2|1) = \frac{P(2,1)}{P_1(1)}=\frac{0}{1/7}=0$  
$P_2(3|1) = \frac{P(3,1)}{P_1(1)}=\frac{0}{1/7}=0$  
When X = 2   
$P_2(1|2) = \frac{P(1,2)}{P_1(2)}=\frac{2/7}{2/7}=1$   
$P_2(2|2) = \frac{P(2,2)}{P_1(2)}=\frac{0}{2/7}=0$  
$P_2(3|2) = \frac{P(3,2)}{P_1(2)}=\frac{0}{2/7}=0$  
When X = 3   
$P_2(1|3) = \frac{P(1,3)}{P_1(3)}=\frac{1/7}{4/7}=1/4$   
$P_2(2|3) = \frac{P(2,3)}{P_1(3)}=\frac{2/7}{4/7}=1/2$     
$P_2(3|3) = \frac{P(3,3)}{P_1(3)}=\frac{1/7}{4/7}=1/4$    

## Q9 MS 6.12 - Page 244
### a.
$$f(y)=\int_y^{2y} \frac{e^{-y/10}}{10y}dx$$
$$f(y)=\frac{e^{-y/10}}{10y}*|x|_y^{2y}$$
$$f(y)=\frac{e^{-y/10}}{10y}*y$$
$$f(y)=\frac{1}{10}*e^{-y/10}$$
This is an exponetial distribution

### b. 
Since it is an exponential distribution,   
We have the mean equal to $1/\lambda = \frac{1}{1/10} = 10$

## Q10 MS 6.14 - Page 245
### a.
$$f(x,y)=\int_0^{inf}\int_0^{x} ce^{-x^2}dydx$$
$$f(x,y)=\int_0^{inf} |yce^{-x^2}|_0^xdx$$
$$f(x,y)=\int_0^{inf} xce^{-x^2}dx$$
$$f(x,y)=c/2$$
$$1=c/2$$
$$c=2$$
(The last intergral is calculated by a calculator)

### b.
$$f(x)=\int_0^{x} 2e^{-x^2}dy$$
$$f(x)=2xe^{-x^2}$$
$$f(x,y)=\int_{-inf}^{inf} f_1(x)dx$$
$$f(x,y)=\int_{0}^{inf} 2xe^{-x^2}dx$$
Let t = x^2, we have $dt=2xdx$   

$$f(x,y)=\int_{0}^{inf} e^{-t}dt$$
$$f(x,y)= |-e^{-x^2}|_0^{inf}$$
As x go to infinitive, $-e^{-x^2}$ go to 0, we have   
$$f(x,y)= 0-(-1)=1$$

### c.
$$f_2(y|x) = \frac{f(x,y)}{f_1(x)}$$
$$f_2(y|x) = \frac{2e^{-x^2}}{2xe^{-x^2}}$$
$$f_2(y|x) = \frac{1}{x}$$

## Q11 MS 6.51 - Page 253
E(XY)   
$$E(XY)=\sum_x \sum_y xyp(x,y)$$
$$E(XY)=(-1)*(-1)*1/12 + (-1)*0*2/12+ (-1)*1*1/12$$
$$+0*(-1)*2/12 + 0*0*0+ 0*1*2/12$$
$$+1*(-1)*1/12 + 1*0*2/12+ 1*1*1/12$$
$$E(XY)= 1/12 - 1/12 -1/12 + 1/12 = 0$$
E(X)   
Looking at the table, We have $p_1(1)=1/3, p_1(2)=1/3, p_1(3)=1/3$    
$$E(X)= \sum_x xp_1(x)$$
$$E(X)= -1* 1/3 + 0*1/3+1*1/3 = 0$$
The same will apply to E(Y), resulting E(Y)=0   
Therefore, the conv is 0    
But, P(x,y) not equal to p_1(x)*p_2(y) so X and Y are not independent

## Q12 MS 6.74 - Page 269
### a.
```{r}
a=1
b=3
n=60
```

Since this is a uniform distibution, we have $𝐸(𝑌\bar{Y}(a+b)/2 = (1+3)/2 = 2$  
We expect 2 parts per milion

### b.
$Var(\bar{Y})=(b-a)^2/12$   
```{r}
mean=2
var=(b-a)^2/12/n
var
```

### c.
As n get bigger, the central limit theorm will kick in. That is, the varibles become normal. The samplings distributed uniformly around the mean

### d.
$$Z=\frac{\bar{Y}-\mu}{\sigma}$$
```{r}
z1=(2.5-mean)/sqrt(var)
z2=(1.5-mean)/sqrt(var)
pnorm(z1)-pnorm(z2)
```

### e.
```{r}
z=(2.2-mean)/sqrt(var)
1-pnorm(z)
```

## Q13. MS 6.90 - Page 273   
X~Bin(20,0.4)
```{r}
n=20
p=0.4
q=1-p
```

### a.
Fewer than 2 meaning less than eqaul to 1
```{r}
a=1 
z1=((a+0.5)-n*p)/(sqrt(n*p*q))
pnorm(z1)
```

### b.
More than half meaning greater than equal to 11   
```{r}
a=11
z2=((a-0.5)-n*p)/(sqrt(n*p*q))  
1-pnorm(z2)
```

### c.
```{r}
pbinom(1,size=n,prob=p) 
1-pbinom(10,size=n,prob=p)
```
The normal distributiont provide a good approximation to the binomial distribution as the results are very close

## Q14 MS 7.108 - Page 362
```{r}
data=read.csv("LEADCOPP.csv")
```
For 99% interval, we have
```{r}
a=0.99
```

### a.
```{r}
t.test(data$LEAD,conf.level = a)
```

### b.
```{r}
t.test(data$COPPER,conf.level = a)
```

### c.
On part a, we have 99% of data of lead lie within (-1.147845, 6.919045)   
On part a, we have 99% of data of copper lie within (0.1518726, 0.6647274) 

### d.
It just mean that 99% of data lie in the interval

## Q15 MS 7.114 - Page 364
```{r}
data = read.csv("SOLARAD.csv")
with(data, t.test(STJOS, IOWA, paired=TRUE, conf.level = 0.95))
```


## Q16 MS 7.116 - Page 364
```{r}
data = read.csv("DIAZINON.csv")
```

### a.
```{r}
with(data, t.test(DAY, NIGHT, paired=TRUE, conf.level = 0.90))
```

### b.
We are assuming the data is normally distributed

### c.
Since the mean of the different is not equal 0, this answer the researcher question. The mean diazinon residue levels differ from day to night.