---
title: "Lab2"
author: "Hoa Hoang"
date: "1/24/2020"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1
```{r}
getwd()
```

## Task 2
```{r}
file=read.csv("EPAGAS.csv")
head(file,6)
```
## Task 3
### Make the object mpg, the number of miles per gallon vector
```{r}
mpg.df=file
mpg = mpg.df$MPG
```

### Transform  the  mpg  variable  to  z
```{r}
z=(mpg-mean(mpg))/sd(mpg)
z
```

### Mean of z = 0
```{r}
round(mean(z))
```

### Variance of z = 1
```{r}
sd(z)^2
```

### Possible outliners
```{r}
z[abs(z)>=2 & abs(z)<=3]
```

### Outliners
```{r}
z[abs(z)>3]
```

### dotplot
```{r}
library (lattice)
mycol = ifelse(abs(z)>3, "Red",
        ifelse(abs(z)>=2 &abs(z)<=3,"Blue", "Black"))  
dotplot(z,col=mycol)
```

## Task 4
### Boxplot (black, notch, title, horizontal)
```{r}
boxplot(z,main="Mile per Gallon",horizontal=TRUE,col="BLACK",notch=TRUE)
```

### Using Chebyshev’s theorem predict the proportion of data within 2 standard deviations of the mean of the mpg data
1-1/4 = 3/4

### Exact proportion within 2 standard deviation of the mean
```{r}
round(length(mpg[abs(z)<2])/length(mpg),4)
```
### Does Chebyshev agree with the data?
Yes, 3/4 means 75%. We have more than 75% of the data within the interval

### Now use the empirical rule, what proportion (according to the rule) of the data should be within 2 standard deviations of the mean?
Empirical rule states that about 95% of the distribution is in the inverval

### How well does it correspond?
We have 96%

### Is the Empirical rule valid in this case? Why?
I would say it is valid as empirical is an estimation and 96% is very-very close to 95%


